Explaining Noord-Holland house prices

### 2023-03-30 README.Rmd
update readme
Start with paper layout

---
title: "Explaining Noord-Holland house prices"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
date: "2023-03-21"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Included data of the research was scraped from Funda. Below map gives an overview of the scope of the data.

@@

The query we used for the Funda-Scraper with below query on 28-03-2023.

```{python eval = FALSE}
scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False, n_pages = 1000)
df = scraper.run()
```
Note that this is not the original Funda-Scraper code underneath. The Function is adjusted to contain additional adress information, compared to the origional function. Code is included in the Scraper.ipynb file to copy the updated package into the site-packages directory of python.

@@

*Distance to public transport (Bus, Subway, and Train)
*Distance to public services (Schools, Universities, Shopping centres)

>>>>

---
title: "Explaining Noord-Holland house prices"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
date: "2023-03-21"

output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

@@

Below the structure, results, and some code of our research can be found.

Kind regards,

Yúri Grings [Linkedin](https://www.linkedin.com/in/yurigrings/), Thomas Nibbering [Linkedin](https://www.linkedin.com/in/thomas-nibbering/), Jitse Ruurd Nauta [Linkedin](https://www.linkedin.com/in/jitseruurdnauta/)

@@

The query below was used to scrape our final research data on (28-03-2023).

```{python eval = FALSE}
scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False,\
n_pages = 1000)
df = scraper.run()
```
Note that this is not the original Funda-Scraper code underneath. The Function is adjusted to contain additional adress information, compared to the origional function. Code is included in the Scraper.ipynb file to copy the updated package into the site-packages directory of python.

@@

* Distance to public transport (Bus, Subway, and Train)
* Distance to public services (Schools, Universities, Shopping centres)
